---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# scerden.geometadb

R data pkg containing tables from `geometadb.sqlite` provided by [GEOmetadb](https://www.bioconductor.org/packages/release/bioc/html/GEOmetadb.html) bioconductor pkg.

## install

```{r, eval = F}
devtools::install_github("scerden/scerden.geometadb")
```


This pkg makes available the following tables:  
```{r, eval = T}
suppressPackageStartupMessages(library(tidyverse))
library(scerden.geometadb)
glimpse(gds)
glimpse(gsm)
glimpse(gse)
glimpse(gpl)
```

## pkg API:

* `find_in_*(x)` finds the observations of table that match pattern `x` in a least 1 variable.
A few built in helper functions to query against each cel of each table (all lower case!):
```{r}
x <- c("top[1|2|3|o]")
find_in_gsm(x)
find_in_gse(x)
x <- c("affy", "nimblegen")
find_in_gpl(x)
# find_in_gds() #TODO
# find_in_gds_subset() #TODO
```

* `harvest_pmids_from_geo(acc)` finds any pubmed ids associated with a GEO accession by
scraping from the GEO accession viewer page:
```{r}
harvest_pmids_from_geo("GSE42528")
```



## pkg creation:

* Prelims  
```{r, eval = F}
use_readme_rmd()
use_data_raw()
use_testthat()
```
* save subset of `geometadb` as `tbl`s  for use in package. see `data-raw/` in pkg source:    
```{r, echo = F}
library(tidyverse)
library(stringr)
tibble(file = list.files("data-raw", pattern = "\\.R$")) %>% 
    separate(file, c("step", "description"), sep = '_') %>% 
    mutate(description = description %>% str_replace('\\.R$', '') %>% str_replace_all('-', ' ')) %>% 
    knitr::kable()
```
* when writing `R/` fxns  
```{r, eval = F}
use_package("tidyr")
use_package("dplyr")
use_package("purrr")
use_package("stringr")
use_package("httr")
use_package("rvest")
```

